\section{Theory}
\subsection{Light emission and absorbtion}

The electron of a specific atom has a discrete spectrum of energy-levels
determined by the potential of the nucleus and the other electrons. When light
interacts with an atom, we are essentially adding energy to the atom, due to
the energy associated with light of a certain frequency $f$,
\begin{equation}
E=hf.
\end{equation} 
Due to the quantum nature of light and electrons, only light of a frequency
corresponding to the difference in energy between two of the discrete energy
levels of the atom can move the electron from the lower energy level to the upper. This process is called absorbtion, and if we send light at a material, the material will absorb light of the wavelengths corresponding to energy transitions of the chemical element composure of the material.

Likewise, when the electron transitions to a lower energy state, the atom will
emit a photon with a frequency corresponding to the transition energy, which is
called emission. Similar to absorbtion, each material will emit light at
frequencies corresponding to it's chemical element composition. One can measure
the spectrum of a material either by absorbing or emitting light, and determine the energy transistions by looking at the spectral lines of the spectrum. For the absorbtion spectrum this will be minima on a wavelength vs. intensity graph. 

The lines that exist due to the differences in the allowed quantum states will have a even finer splitting due to fine and hyperfine structure, which arises due to the dipole moment of the electron and the nucleus respectively. 


\subsubsection{Blackbody radiation}
All matter emits electromagnetic radiation, when it has a temperature above absolute zero. This radiative distribution of entropy is called thermal radiation and is a spontaneous process.

Similarly, all matter absorbs electromagnetic radiation to some degree. In addition, a blackbody is an object that absorbs all radiation of all wavelengths that falls upon it. Furthermore, at thermal equillibrium a blackbody emits a characteristic frequency distribution, which is temperature depended. The relationship between the spectral radiance density $B_f$ for a certain frequency $f$ and the temperature of a black body is given by plancks law:
%
\begin{align}
B_{f}(T)= \frac{2hf^3}{c^2}\frac{1}{\exp(\frac{hf}{kT})-1}
\label{planck}
\end{align}

Where $c$ is the speed of light, $h$ is Planck's constant, $k$ is Boltzmann's
constant and $T$ is the temperature. For each frequency or wavelength $\lambda$
(related by $\lambda f = c$), there is a certain temperature where the spectral
radiance density will reach its maxima or vise versa, eg. for each temperature
there is a characteristic wavelength where the spectral radiance density has a maxima. The relationship between this temperature and wavelength is inversely proportional, and is given by Wien's displacement law:
%
\begin{align}
\lambda_{max}T=\SI{2.897 e-3}{\kelvin \meter}
\label{eq:wien}
\end{align}

\begin{table}[h]
	\begin{tabular}[h]{ccc}
		\toprule
		\multicolumn{3}{c}{title}\\
		\midrule
		Obs. Wavelength & Lower level & Upper level  \\
		\multirow{2}{*}{462} & 12  & 6 \\
		 & 8 & 9 \\
		\bottomrule
	\end{tabular}
\end{table}
